Certified Knowledge Compilation \\ with Application to Verified Model Counting

### 2023-03-20 doc/mc-paper.tex
Edits

Generating proofs of unsatisfiability in SAT solvers has a long
tradition~\cite{ZhangMalik} and has become widely accepted due to the
formulation of clausal proof systems for which proofs can readily be
generated and efficiently checked
\cite{RAT,wetzler14_drattrim}.
A number formally verified checkers for this task have been developed within different frameworks~\cite{cruz-cade-2017,Heule:et:al:17,Lammich:20,Tan:2021}.
The associated proofs add clauses while preserving satisfiability until the empty clause is derived.
By contrast, our proofs construct a new propositional formula, and we must verify both that it
is partitioned and that it is equivalent to the input formula.
This requires verifying additional proof steps, including clause deletion steps, and subtle invariants, as described in
Sections~\ref{sect:crat} and \ref{section:formally-verified-toolchain}.

>>>>

Generating proofs of unsatisfiability in SAT solvers has a long
tradition~\cite{ZhangMalik} and has become widely accepted due to the
formulation of clausal proof systems for which proofs can readily be
generated and efficiently checked
\cite{RAT,wetzler14_drattrim}.
A number of formally verified checkers have been developed within different verification frameworks~\cite{cruz-cade-2017,lrat,Lammich:20,Tan:2021}.
The associated proofs add clauses while preserving satisfiability until the empty clause is derived.
By contrast, our proofs construct a new propositional formula, and we must verify both that it
is partitioned and that it is equivalent to the input formula.
This requires verifying additional proof steps, including clause deletion steps, and subtle invariants, as described in
Sections~\ref{sect:crat} and \ref{section:formally-verified-toolchain}.
